Market-based Mechanisms for Resource Scheduling

### 2013-12-14 paper/paper.tex
Organization/formating fixes

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Paul Christiano
% 2nd. author
\alignauthor
Frank Li
% 3rd. author
\alignauthor
Richard Shin
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Lawrence P. Leipuner\\
%       \affaddr{Brookhaven Laboratories}\\
%       \affaddr{Brookhaven National Lab}\\
%       \affaddr{P.O. Box 5000}\\
%       \email{lleipuner@researchlabs.org}
%% 5th. author
%\alignauthor Sean Fogarty\\
%       \affaddr{NASA Ames Research Center}\\
%       \affaddr{Moffett Field}\\
%       \affaddr{California 94035}\\
%       \email{fogartys@amesres.org}
%% 6th. author
%\alignauthor Charles Palmer\\
%       \affaddr{Palmer Research Laboratories}\\
%       \affaddr{8600 Datapoint Drive}\\
%       \affaddr{San Antonio, Texas 78229}\\
%       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Large-scale computing clusters offer potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated \emph{fairness}
criterions, such as dominant resource fairness (DRF), which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings---when dealing with inhomogeneous resources, time-varying
demands, requirements for data locality, etc.---these systems cease to be either
efficient or non-manipulable.

We implement these ideas in the Mesos cluster manager, along with microeconomic
``agents'' which allow traditional Mesos clients to interact seamlessly with our
modified implementation. We show that the computational and communication
overhead proposed by our system is manageable and that its performance compares
favorably to existing approaches (particularly DRF) even when users don’t
provide any meaningful price information. Moreover, we show that when accurate
economic data is available our system is able to achieve substantially higher
social welfare than DRF. Finally, we discuss a number of examples where this
functionality may be useful even in applications where the end-users of the
system don't have to think about economics at all, and instead prices are
generated algorithmically as a principled way to accommodate constraints that
are currently managed in an ad hoc way.
\end{abstract}

@@

\section{Introduction}
\subsection{Overview}
We consider an environment in which a single cluster is used for a variety of
tasks, which may have very different demands for resources. For example, a
company might run research tasks in the same cluster as production web services,
in order to make use of computational resources which would otherwise lie idle
when web traffic is low. In general, running different tasks in the same cluster
has the promise of improving utilization and reducing overhead.

@@

\subsection{Microeconomic methods}
In this paper we confront the challenge of modifying Mesos to provide more
robust efficiency guarantees, without compromising its agnosticism regarding the
nature of different frameworks’ desiderata. We propose \emph{price signals} as a
mechanism for accomplishing this; instead of accepting or rejecting a resource
offer, a framework can express its preferences by assigning a \emph{willingness
to pay} for that resource, and Mesos can give the resources to whichever
frameworks are most willing to pay.

@@

\subsection{Guide to the paper}
In section 2, we make the theoretical case for using microeconomic methods. We
provide a litany of examples in which existing approaches, and in particular
DRF, fail to be either efficient or strategy-proof, and describe examples of
strategic behavior in Mesos. We discuss a number of examples in which economic
data generated \emph{within} the system could be useful, and compare this approach to a
number of ad hoc approaches currently pursued to solve similar problems.

In section 3, we describe our protocol and the most important design decisions
we made. In particular, we describe the mechanisms we used to ensure that our
protocol remains backwards-compatible, and can be applied without any change to
the clients’ code.

In section 4, we describe our implementation of this protocol within Mesos.

In section 5, we report on experimental comparisons between our results and
existing approaches: (a) we evaluate the computational and communication
overhead of our approach and show that it is manageable, (b) we compare our
system in ``backwards-compatibility mode,'' without any economic information
whatsoever, to DRF, and show that it performs comparably whether judged by
utilization or fairness, (c) we examine a number of cases in which economic
information is available; we show that in general our algorithms achieve higher
social efficiency than DRF, and provide natural examples in which DRF fails to
be Pareto efficient.

\section{The case for microeconomic scheduling}
\subsection{Scheduling is hard}
Consider the following typical situations within a cluster:
\begin{enumerate}
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}
In each of these examples, clients of the cluster have preferences over
allocations which are difficult to precisely express. It would be possible but
difficult to cover just these cases, but the reader can doubtless generate many
similar cases, and as the environment changes the nature of these constraints is
likely to continue to change as well.

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The acm\_proc\_article-sp document class file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

>>>>

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Paul Christiano, Frank Li, Richard Shin \\
% 2nd. author
% 3rd. author
\email{\{paulchristiano, frankli, ricshin\}@cs.berkeley.edu}
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Lawrence P. Leipuner\\
%       \affaddr{Brookhaven Laboratories}\\
%       \affaddr{Brookhaven National Lab}\\
%       \affaddr{P.O. Box 5000}\\
%       \email{lleipuner@researchlabs.org}
%% 5th. author
%\alignauthor Sean Fogarty\\
%       \affaddr{NASA Ames Research Center}\\
%       \affaddr{Moffett Field}\\
%       \affaddr{California 94035}\\
%       \email{fogartys@amesres.org}
%% 6th. author
%\alignauthor Charles Palmer\\
%       \affaddr{Palmer Research Laboratories}\\
%       \affaddr{8600 Datapoint Drive}\\
%       \affaddr{San Antonio, Texas 78229}\\
%       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}

\end{abstract}

@@

\section{Introduction}
\label{sec:intro}

Large-scale computing clusters offer potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated \emph{fairness}
criterions, such as dominant resource fairness (DRF), which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings---when dealing with inhomogeneous resources, time-varying
demands, requirements for data locality, etc.---these systems cease to be either
efficient or non-manipulable.

We implement these ideas in the Mesos cluster manager, along with microeconomic
``agents'' which allow traditional Mesos clients to interact seamlessly with our
modified implementation. We show that the computational and communication
overhead proposed by our system is manageable and that its performance compares
favorably to existing approaches (particularly DRF) even when users do not
provide any meaningful price information. Moreover, we show that when accurate
economic data is available our system is able to achieve substantially higher
social welfare than DRF. Finally, we discuss a number of examples where this
functionality may be useful even in applications where the end-users of the
system don't have to think about economics at all, and instead prices are
generated algorithmically as a principled way to accommodate constraints that
are currently managed in an ad hoc way.

\subsection{Guide to the paper}

In section \ref{sec:overview}, we provide a brief overview of Mesos and how it
could incorporate microeconomic mechanisms.

In section \ref{sec:case}, we make the theoretical case for using microeconomic methods. We
provide a litany of examples in which existing approaches, and in particular
DRF, fail to be either efficient or strategy-proof, and describe examples of
strategic behavior in Mesos. We discuss a number of examples in which economic
data generated \emph{within} the system could be useful, and compare this approach to a
number of ad hoc approaches currently pursued to solve similar problems.

In section \ref{sec:design}, we describe our protocol and the most important design decisions
we made. In particular, we describe the mechanisms we used to ensure that our
protocol remains backwards-compatible, and can be applied without any change to
the clients’ code.

In section \ref{sec:eval}, we report on simulated comparisons between our
design and existing approaches: (a) we evaluate the computational and communication
overhead of our approach and show that it is manageable, (b) we compare our
system in ``backwards-compatibility mode,'' without any economic information
whatsoever, to DRF, and show that it performs comparably whether judged by
utilization or fairness, (c) we examine a number of cases in which economic
information is available; we show that in general our algorithms achieve higher
social efficiency than DRF, and provide natural examples in which DRF fails to
be Pareto efficient.

\section{Overview}
\label{sec:overview}

We consider an environment in which a single cluster is used for a variety of
tasks, which may have very different demands for resources. For example, a
company might run research tasks in the same cluster as production web services,
in order to make use of computational resources which would otherwise lie idle
when web traffic is low. In general, running different tasks in the same cluster
has the promise of improving utilization and reducing overhead.

@@

\subsection{Microeconomic methods}
In this paper we confront the challenge of modifying Mesos to provide more
robust efficiency guarantees, without compromising its agnosticism regarding the
nature of different frameworks' desiderata. We propose \emph{price signals} as a
mechanism for accomplishing this; instead of accepting or rejecting a resource
offer, a framework can express its preferences by assigning a \emph{willingness
to pay} for that resource, and Mesos can give the resources to whichever
frameworks are most willing to pay.

@@

\section{The case for microeconomic scheduling}
\label{sec:case}

\subsection{Scheduling is hard}
Consider the following typical situations within a cluster:
\begin{enumerate}
  \item Some clients have regular throughput and flexible deadlines, while some
    clients have hard real-time constraints and variable traffic.
  \item Different tasks make use of different characteristics of hardware on
    machines in the cluster, for example high ratios of RAM to CPU on a
    particular machine, or GPUs or other hardware that is available on only
    certain machines.
  \item Tasks require data which is located on disk or even in memory somewhere
    in the cluster, and co-locating the tasks with the data improves
    performance.
\end{enumerate}
In each of these examples, clients of the cluster have preferences over
allocations which are difficult to precisely express. It would be possible but
difficult to cover just these cases, but the reader can doubtless generate many
similar cases, and as the environment changes the nature of these constraints is
likely to continue to change as well.

@@

\section{Market-based Mechanism Design}
\label{sec:design}

\section{Evaluation}
\label{sec:eval}

\section{Future Works}
\label{sec:future}

\section{Conclusion}
\label{sec:conclusion}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The acm\_proc\_article-sp document class file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}
